MRP Case Study

### 2020-02-14 Code/mrp/Case Study .Rmd
Now that we have successfully sampled from our postratification code, we need to start building a logistic linear model.

We will be modeling our populations `satisfaction`. This will eventually translate into measuring service severity when we apply our model to our real data. We will be looking at common characteristics like `gender`, `ethnicity`, `income`, `age`, and `state`.

@@

```{r}
mrp_sim <- simulate_mrp_data(n=1200)
sample <- mrp_sim[["sample"]]

print(sample)
```

@@

// Generate data according to the hierarchical regression.
generated quantities {
  matrix[K, (I - 1)] alpha;              // Matrix of observation-level brand coefficients.
  vector[K] beta;                        // Vector of observation-level price coefficients.
  real gamma;                            // Mean of the population model.
  real<lower=0> tau;                     // Variance of the population model.
  real<lower=0> sigma;                   // Variance of the observation model.

  vector[N] mu;                          // Declare mu for linear model.
  real cat_pref[N];                        // Vector of observations.

@@

  // Draw parameter values and generate data.
  for (k in 1:K) {
    for (i in 1:(I - 1)) {
      alpha[k, i] = normal_rng(gamma, tau);
    }
    beta[k] = normal_rng(gamma, tau);
  }
  for (n in 1:N) {
    mu[n] = alpha[male[n], eth[n]] + beta[male[n]] * age[n] + beta[male[n]] * 
    income[n] + beta[male[n]] * state[n];
    cat_pref[n] = normal_rng(mu[n], sigma);
  }
}

@@

```{r}
sim_values <- list(
  N = 6300,                                       # Number of observations.
  K = 2,                                         # Number of groups.
  I = 65,                                         # Number of observation-level covariates.

@@

  gamma_mean = 0.5,                              # Mean for the hyperprior on gamma.
  gamma_var = 0.2,                               # Variance for the hyperprior on gamma.
  tau_min = 0,                                   # Minimum for the hyperprior on tau.
  tau_max = .1,                                   # Maximum for the hyperprior on tau.
  sigma_min = 0,                                 # Minimum for the hyperprior on tau.
  sigma_max = .1                                  # Maximum for the hyperprior on tau.
)
# Generate data.
sim_data <- stan(
  file = here::here("Code/mrp/generate_data.stan"),
  data = sim_values,
  iter = 10,
  chains = 1,
  seed = 42,
  algorithm = "Fixed_param"
)
```

```{r}
# Extract the simulated data.
prior_pc <- tibble(
  cat_pref = as.vector(extract(sim_data)$cat_pref)
)
# Plot the prior predictive distribution.
prior_pc %>% 
  ggplot(aes(x = cat_pref)) +
  geom_density()
```

```{r}
# # Specify data.
# data <- list(
#   N = nrow(true_popn),                     # Number of observations.
#   K = 2,                    # Number of groups.
#   I = 65,                                # Number of observation-level covariates.
#   
#   cat_pref = true_popn$cat_pref,               # Vector of observations.
#   male = as.numeric(as.factor(true_popn$male)),            # Vector of group assignments.
#   eth = true_popn$eth,       # Vector of brands covariates.
#   age = true_popn$age,        # Vector of price covariates.
#   income = true_popn$income,
#   state = true_popn$state,
#   
#   gamma_mean = 0.5,                                # Mean for the hyperprior on gamma.
#   gamma_var = .2,                                 # Variance for the hyperprior on gamma.
#   tau_min = 0,                                   # Minimum for the hyperprior on tau.
#   tau_max = 1,                                   # Maximum for the hyperprior on tau.
#   sigma_min = 0,                                 # Minimum for the hyperprior on tau.
#   sigma_max = 1                                 # Maximum for the hyperprior on tau.
# )
# # Calibrate the model.
# model03 <- stan(
#   file = here::here("Code/mrp/hierarchical_model.stan"),
#   data = data,
#   control = list(adapt_delta = 0.99),
#   seed = 42
# )
```

```{r}
# Posterior predictive check.
# post_pc03 <- tibble(
#   # Extract the posterior predicted values.
#   intent = as.vector(extract(model03)$cat_pref_pc)
# )
# # Plot the posterior predictive distribution.
# ggplot(post_pc03, aes(x = intent)) +
#   geom_histogram() +
#   xlim(1, 10) 
# ggplot(purchase_intent, aes(x = intent)) +
#   geom_histogram() +
#   xlim(1, 10) 
```

```{r}
# model03 %>%
#   gather_draws(alpha[n, i]) %>%
#   unite(.variable, .variable, n, i) %>%
#   ggplot(aes(x = .value, y = .variable)) +
#   geom_halfeyeh(.width = .95) +
#   facet_wrap(
#     ~ .variable,
#     nrow = data$K,
#     ncol = (data$I - 1),
#     scales = "free"
#   )
```

```{r}
# Plot the betas.
# model03 %>%
#   gather_draws(beta[i]) %>%
#   unite(.variable, .variable, i) %>%
#   ggplot(aes(x = .value, y = .variable)) +
#   geom_halfeyeh(.width = .95) +
#   facet_wrap(
#     ~ .variable,
#     nrow = data$K,
#     ncol = 1,
#     scales = "free"
#   )
```

@@

```{r eval = FALSE}
poststrat_prob <- posterior_prob %*% poststrat$N / sum(poststrat$N)
model_popn_pref <- c(mean = mean(poststrat_prob), sd = sd(poststrat_prob))
round(model_popn_pref, 3)
```

@@

```{r eval = FALSE}
sample_popn_pref <- mean(sample$satisfaction)
round(sample_popn_pref, 3)

>>>>

We will be modeling our populations `service_failure`. This will eventually translate into measuring service severity when we apply our model to our real data. We will be looking at common characteristics like `gender`, `ethnicity`, `income`, `age`, and `state`.

@@

```{r}

mrp_sim <- simulate_mrp_data(n=1200)
sample <- mrp_sim[["sample"]]

head(sample)

We now have need for a logistic regresson model in order to predict a binary outcome for 'service_failure' so we will make a hierarchal logit model

# Hierarchal Logit Model

 data {
   // Define variables in data
   // Number of observations (an integer)
   int<lower=0> N;
   // Number of parameters
   int<lower=0> p;
   // Variables
   int death[N];
   int<lower=0>  qsmk[N];
   int<lower=0>  sex[N];
   real<lower=0> age[N];
   int<lower=0>  race[N];
   real<lower=0> smokeyrs[N];
 }

 parameters {
   // Define parameters to estimate
   real beta[p];
 }

 transformed parameters  {
   // Probability trasformation from linear predictor
   real<lower=0> odds[N];
   real<lower=0, upper=1> prob[N];

   for (i in 1:N) {
     odds[i] <- exp(beta[1] + beta[2]*qsmk[i] + beta[3]*sex[i] + beta[4]*age[i] + beta[5]*race[i] + beta[6]*smokeyrs[i]);
     prob[i] <- odds[i] / (odds[i] + 1);
   }
 }

 model {
   // Prior part of Bayesian inference (flat if unspecified)

  // Likelihood part of Bayesian inference
    death ~ bernoulli(prob);
}

@@

// Generate data according to the hierarchical regression.
generated quantities {
  matrix[K, (I - 1)] alpha;              // Matrix of observation-level gender coefficients.
  vector[K] beta;                        // Vector of all other observation-level coefficients.
  real gamma;                            // Mean of the population model.
  real<lower=0> tau;                     // Variance of the population model.
  real<lower=0> sigma;                   // Variance of the observation model.

  vector[N] mu;                          // Declare mu for linear model.
  real service_failure[N];                        // Vector of observations.

@@

  // Draw parameter values and generate data.
  for (k in 1:K) {
    for (i in 1:(I - 1)) {
      alpha[k, i] = normal_rng(gamma, tau);
    }
    beta[k] = normal_rng(gamma, tau);
  }
  for (n in 1:N) {
    mu[n] = alpha[male[n], eth[n]] + beta[male[n]] * age[n] + beta[male[n]] * 
    income[n] + beta[male[n]] * state[n];
    service_failure[n] = normal_rng(mu[n], sigma);
  }
}

@@

```{r}

sim_values <- list(
  N = 6300,                                       # Number of observations.
  K = 2,                                         # Number of groups.
  I = 65,                                         # Number of observation-level covariates.

@@

  gamma_mean = 0.5,                              # Mean for the hyperprior on gamma.
  gamma_var = 0.2,                               # Variance for the hyperprior on gamma.
  tau_min = 0,                                   # Minimum for the hyperprior on tau.
  tau_max = .1,                                   # Maximum for the hyperprior on tau.
  sigma_min = 0,                                 # Minimum for the hyperprior on tau.
  sigma_max = .1                                  # Maximum for the hyperprior on tau.
)
# Generate data.
sim_data <- stan(
  file = here::here("Code/mrp/generate_data.stan"),
  data = sim_values,
  iter = 10,
  chains = 1,
  seed = 42,
  algorithm = "Fixed_param"
)

```{r}

# Extract the simulated data.
prior_pc <- tibble(
  service_failure = as.vector(extract(sim_data)$service_failure)
)
# Plot the prior predictive distribution.
prior_pc %>% 
  ggplot(aes(x = service_failure)) +
  geom_density()

```{r echo=FALSE}

# # Specify data.
# data <- list(
#   N = nrow(true_popn),                     # Number of observations.
#   K = 2,                    # Number of groups.
#   I = 65,                                # Number of observation-level covariates.
#   
#   cat_pref = true_popn$cat_pref,               # Vector of observations.
#   male = as.numeric(as.factor(true_popn$male)),            # Vector of group assignments.
#   eth = true_popn$eth,       # Vector of brands covariates.
#   age = true_popn$age,        # Vector of price covariates.
#   income = true_popn$income,
#   state = true_popn$state,
#   
#   gamma_mean = 0.5,                                # Mean for the hyperprior on gamma.
#   gamma_var = .2,                                 # Variance for the hyperprior on gamma.
#   tau_min = 0,                                   # Minimum for the hyperprior on tau.
#   tau_max = 1,                                   # Maximum for the hyperprior on tau.
#   sigma_min = 0,                                 # Minimum for the hyperprior on tau.
#   sigma_max = 1                                 # Maximum for the hyperprior on tau.
# )
# # Calibrate the model.
# model03 <- stan(
#   file = here::here("Code/mrp/hierarchical_model.stan"),
#   data = data,
#   control = list(adapt_delta = 0.99),
#   seed = 42
# )

```{r echo=FALSE}
# Posterior predictive check.
# post_pc03 <- tibble(
#   # Extract the posterior predicted values.
#   intent = as.vector(extract(model03)$cat_pref_pc)
# )
# # Plot the posterior predictive distribution.
# ggplot(post_pc03, aes(x = intent)) +
#   geom_histogram() +
#   xlim(1, 10) 
# ggplot(purchase_intent, aes(x = intent)) +
#   geom_histogram() +
#   xlim(1, 10) 
```

```{r echo=FALSE}
# model03 %>%
#   gather_draws(alpha[n, i]) %>%
#   unite(.variable, .variable, n, i) %>%
#   ggplot(aes(x = .value, y = .variable)) +
#   geom_halfeyeh(.width = .95) +
#   facet_wrap(
#     ~ .variable,
#     nrow = data$K,
#     ncol = (data$I - 1),
#     scales = "free"
#   )
```

```{r echo=FALSE}
# Plot the betas.
# model03 %>%
#   gather_draws(beta[i]) %>%
#   unite(.variable, .variable, i) %>%
#   ggplot(aes(x = .value, y = .variable)) +
#   geom_halfeyeh(.width = .95) +
#   facet_wrap(
#     ~ .variable,
#     nrow = data$K,
#     ncol = 1,
#     scales = "free"
#   )
```

@@

```{ echo=FALSE}
poststrat_prob <- posterior_prob %*% poststrat$N / sum(poststrat$N)
model_popn_pref <- c(mean = mean(poststrat_prob), sd = sd(poststrat_prob))
round(model_popn_pref, 3)
```

@@

```{ echo=FALSE}
sample_popn_pref <- mean(sample$satisfaction)
round(sample_popn_pref, 3)
